\section*{Acknowledgments}

Any graduate thesis is a collaboration between the writer and the people around them who have supported them over the years. So I'd like to take a moment to recognize all those whose collaboration and help has made this thesis possible. 

First, I would like to thank my advisor, Jeff Peterson, who has always been a great support and guide through the perils of graduate school. Thanks for helping me find the adventurous side of cosmology. I can't believe I get to travel the world and do science at the same time.

Second, I would like to thank all of the professors, post-docs and students who have worked on the SCI-HI project over the past several years. I would particularly like to acknowledge the hard work of my fellow graduate student, Jose-Miguel Jauegui-Garcia, who was my co-conspirator in developing much of the SCI-HI system. Also, Aravind Natarajan, the post-doc who worked with me on the data analysis side of the SCI-HI project. Some of the other folks who have worked hard to make the SCI-HI project a reality include, but are not limited to; Omar Lopez-Cruz, Edgar Castillo, Amy Stetten, Alma Gonzalez, Taylor Merritt, Aleksander Popstefanija, and Bruce Taylor. 

Third, I would like to thank all of my collaborators on my other research projects who helped me to succeed and develop skills that I have used in my thesis. These collaborations include the GBT-IM team, the CHIME team, the Hydrogen Sky Planetarium Show team and many others. 

Fourth, I would like to thank all of the students, post-docs and professors around the Physics department here at Carnegie Mellon University; especially those in the McWilliams Center for Cosmology. I never would have survived without the support, advice and feedback I have recieved from all of you. Special thanks to the members of my thesis committee, who helped keep me on track and get to this point. 

Fifth, I would like to thank all of my extended support network who have helped me through this roller coaster. Thanks to all of my SWEsters, who constantly remind me that anything is possible and that women in STEM are awesome. 

Finally, I would like to thank all of my family for their constant support and encouragement. Special thanks to Mom, Dad, Josh, Abe, Dave and Tim for putting up with my craziness when I needed it most. Look, look, I did it!

